### 2022-06-07 omicron-generation.tex
oops!

Serial interval data are taken from \cite{backer2021omicron}.
Infector-infectee pairs were identified through contact tracing, and their symptom onset dates were reported through a national surveillance database.
Serial intervals were then calculated by taking the difference between symptom onset dates of the infector and the infectee.
In order to ensure independence between serial intervals, one infectee was chosen at random for each infector in the original analysis.
See original article for additional details of data collection.

@@

Finally, there are several sources of biases in serial-interval data that we did not consider.
For example, the direction of transmission is particularly difficult to establish for SARS-CoV-2 due to pre-symptomatic transmission.
Other sources of information, such as exposure history and positive test results, can help resolve uncertainties but are imperfect.
Serial interval data also depend on the ability of infected individuals to accurately recall when their symptoms started.
Future studies may explore how these biases affect the inference of generation intervals from serial intervals.
While comparisons of incubation-period and serial-interval distributions can shed insight on pathogen dynamics, both distributions typically do not account for the dynamics of asymptomatic infections; neglecting these differences can further bias estimates of transmissibility of a pathogen \citep{park2020time}.

>>>>

Serial-interval data are taken from \cite{backer2021omicron}.
Infector-infectee pairs were identified through contact tracing, and their symptom onset dates were reported through a national surveillance database.
Serial intervals were then calculated by taking the difference between symptom onset dates of the infector and the infectee.
In order to ensure independence between serial intervals, one infectee was chosen at random for each infector in the original analysis.
See original article for additional details of data collection.

@@

Finally, there are several sources of biases in serial-interval data that we did not consider.
For example, the direction of transmission is difficult to establish for SARS-CoV-2 due to pre-symptomatic transmission.
Other sources of information, such as exposure history and positive test results, can help resolve uncertainties but are imperfect.
Serial-interval data also depend on the ability of infected individuals to accurately recall when their symptoms started.
Future studies may explore how these biases affect the inference of generation intervals from serial intervals.
While comparisons of incubation-period and serial-interval distributions can shed insight on pathogen dynamics, both distributions typically do not account for the dynamics of asymptomatic infections; neglecting these differences can further bias estimates of transmissibility of a pathogen \citep{park2020time}.
